---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Mets

<!-- badges: start -->
<!-- badges: end -->

The goal of Mets is to explore the arts of The Metropolitan Museum of Art.

## Installation

You can install the released version of Mets from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Mets")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Qwhj0911/Mets")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Mets)
## arts_overview

## arts_images
```

There is a demo of the two functions
```{r}
# arts_overview(q = "french", isOnView = "true", hasImages = "true", medium = "Silk")

```

Input the ObjectIDs you got from the overview function
```{r}
# arts_images(c(197742, 197743))

```

## arts_overview
There are 7 parameters: "q", "isOnView", "medium", "hasImages", "geoLocation", "dateBegin", and "dateEnd". The q is the main query, which is required. Others can be ignored, but the more conditions you input, the less results it returns, which will make the process faster. eg. just try, q = "sunflowers" or "China"; isOnView = "true"; medium = "Silk".

The result shows a head of first 6 observations, and the whole dataframe will automatically be saved as "arts_overview.csv" file.


## Keep in mind
The more specific parameters you input using arts_overview, the less objects it returns, which helps to extract data smoothly, since there are more than 470,000 artworks in the Mets database.

When the result you may get exceeds 100 or so, the process will become pretty slow, or the Rstudio may collapse, or the computer even freeszes that definitely is not what you want.

For the arts_overview function, each parameter is case sensitive, and a quotation sigh is required.



